%------------------------------------------------------------------
%	SECTION TITLE
%------------------------------------------------------------------
\cvsection{Experience}


%------------------------------------------------------------------
%	CONTENT
%------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Information Technology} % Job title
    {Cambria Adara Properties, LLC.} % Organization
    {San Antonio, Texas} % Location
    {Nov. 2008 - Jan. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
			Provided service to several night clubs throughout the
			state of Texas.
		}
        \item {
			Maintained CCTV systems and local area networks.
		}
		\item {
			Remotely managed company computers through VNC and
			Teamviewer.
		}
		\item {
			Ensured compliance with payment card industry
			requirements.
		}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sole Proprietor \& Software Engineer} % Job title
    {Paladin Technologies, DBA.} % Organization
    {Rockport, Texas} % Location
    {Jan. 2014 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
			Provided information technology services to Cambria
			Adara Properties, LLC. as an independent contractor.
		}
        \item {
			Upgraded ATM machine hardware and software at approximately
			50 locations to ensure EMV compliance.
		}
        \item {
			Prototyped a centralized smart home control system
			based on the Raspberry Pi for a client overseas.
		}
        \item {
			Created circuit board designs using CAD software.
		}
        \item {
			Designed an open source digital signage solution
			for the Raspberry Pi.
		}
        \item {
			Developed firmware in C/C++ for the Espressif
			ESP8266 and ESP32.
		}
      \end{cvitems}
    }
\end{cventries}

%---------------------------------------------------------

\begin{cvskills}
	\cvskill{Skills}{
		Python, Tensorflow, Keras, C++, Java,
		Linux/BSD, SQL, Latex,
		MS Office, Docker, Git, NumPy, Mathematica,
		Jupyter
	}
\end{cvskills}

%---------------------------------------------------------
