%-----------------------------------------------------------------
%	SECTION TITLE
%-----------------------------------------------------------------
\cvsection{Extracurriculars}

%-----------------------------------------------------------------
%	CONTENT
%-----------------------------------------------------------------

%---------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
  	{Student volunteer for UTD faculty} % Job title
		{
			\href{https://github.com/TidalPaladin/tiny-imagenet-demo}
			{Tiny ImageNet Demonstrations \faGithubSquare}
		} % Organization
    {Richardson, Texas} % Location
  	{May. 2018 - Sep. 2018} % Date(s)
	{
	\begin{cvitems}
		\item {
				Developed scripts to produce a lower resolution version of
				ImageNet.
		}
		\item {
				Implemented vision networks based on Resnet and
				Inception-Resnet for dominant object classification.
		}
		\item {
				Achieved 53\% top-1 validation accuracy in 24 hours of
				training using an Inception variant.
		}
	\end{cvitems}
	}
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
  	{Predicting future trends with deep learning} % Job title
		{
			\href{https://github.com/TidalPaladin/trader}
			{Neural Stock Prediction \faGithubSquare}
		} % Organization
    {Richardson, Texas} % Location
  	{May. 2018 - Aug. 2018} % Date(s)
	{
	\begin{cvitems}
		\item {
				Implemented a Tensorflow compatible preprocessing pipeline using
				Apache Spark capable of handling 8,000+ securities.
		}
		\item {
				Designed a convolutional encoder with an attention-based
				classification head to predict discretized future percent
				change.
		}
		\item {
				Achieved 51\% overall top-1 validation accuracy, with ongoing work to
				examine accuracy over only high confidence predictions.
		}
	\end{cvitems}
	}
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Low Cost Digital Radiographs} % Job title
		{
			\href{https://github.com/TidalPaladin/xray-controller.git}
			{X-Ray Photography \faGithubSquare}
		} % Organization
    {Rockport, Texas} % Location
    {May. 2016 - Aug. 2018} % Date(s)
	{
	\begin{cvitems}
		\item {
			Designed an apparatus to safely capture high resolution
			digital radiographs using a DLSR at a low price point.
		}
		\item {
			Implemented an beam control system that included multiple
			redundant safety mechanisms.
		}
		\item {
			Automated the capture of radiographs using MQTT and Python
			to coordinate multiple pieces of hardware.
		}
		\item {
			Explored post-processing techniques to remove X-Ray induced
			noise from captured images.
		}
	\end{cvitems}
	}
%---------------------------------------------------------
%---------------------------------------------------------
  %\cventry
  	%{Welcome Center Volunteer} % Job title
    %{Driscoll Children's Hospital} % Organization
    %{Corpus Christi, Texas} % Location
    %{Mar. 2016 - May 2017} % Date(s)
	%{
	%\begin{cvitems} % Description(s) of tasks/responsibilities
		%\item {
			%227 hours of service
		%}
		%\item {
			%Checked in hospital visitors
		%}
	%\end{cvitems}
	%}
%---------------------------------------------------------
%---------------------------------------------------------
  %\cventry
  	%{Airplane - Single Engine - Land} % Job title
    %{Private Pilot's Certificate} % Organization
    %{Corpus Christi, Texas} % Location
    %{Aug. 2010 - Aug 2011} % Date(s)
	%{\phantom{x}}
%---------------------------------------------------------
\end{cventries}
%---------------------------------------------------------
